---
title: "HHS-Protect Data Analysis"
author: "Jeff Cegan"
date: "2022-03-17"
output: time series graphs for PPT
---

Tools for working with COVID-19 Forecast Hub data: covidHubUtils R package
http://reichlab.io/covidHubUtils/articles/covidHubUtils-overview.html
```{r}
# BEFORE RUNNING THIS NOTEBOOK, UNCOMMENT THIS CELL TO RUN THE COMMANDS BELOW
#devtools::install_github("reichlab/zoltr")
#devtools::install_github("reichlab/covidHubUtils")
```
# Section 1: Imports and Inputs
## Import Libraries
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(zoo)
library(readxl)
library(lubridate)
library(covidHubUtils)
library(doParallel)
library(tidyverse)
library(openxlsx)


theme_set(theme_bw() + theme( legend.position="bottom" ) +
             theme( text = element_text(size=16, face="bold")) +
            theme(axis.text.x=element_text(angle=60, hjust=1)))

R1states <- c('CT', 'MA', 'ME', 'NH', 'RI', 'VT') # FEMA Region 1
R1stfips <- c('09','25','23','33','44','50') #, '36') # FIPS of states in New England + NY
R1HRR <- c(109,110,111,221,222,227,230,231,281,282,295,364,424) # Codes for R1 HRRs

#R2states <- c('NY', 'NJ', 'PR')
#R3states <- c('DE', 'DC', 'MD', 'PA', 'VA', 'WV')
#R4states <- c('AL', 'FL', 'GA', 'KY', 'MS', 'NC', 'SC', 'TN') # Region 4
#R5states <- c('IL', 'IN', 'MI', 'MN', 'OH', 'WI')
#R6states <- c('TX', 'AR', 'LA', 'NM', 'OK')
#R7states <- c('IA', 'KS', 'MO', 'NE', '')
#R8states <- c('CO', 'MT', 'ND', 'SD', 'UT', 'WY')
#R9states <- c('AZ', 'CA', 'HI', 'NV') # Some Islands Missing Abbreviations
#R10states <- c('AK', 'ID', 'OR', 'WA')

#Selectstates <- c('FL', 'MS', 'TX', 'CA') # Non-New England States to Compare

target_states <- R1states
target_statefips <- R1stfips
target_hrrs <- R1HRR
```


## Set Important Variables
```{r}
# Date most hospitals reported for HHS dataset
# Typically this is the Wednesday of the previous week
date_most_hospitals_reported <- '2022-03-09'

# CDC Forecast Date: Date of most recent CDC ensemble updates
# Typically this is every Monday night
date_latest_forecast <- '2022-03-14'

# JHU Count date: Date of the most recent case counts for JHU
# Typically this is previous Friday
date_case_count <- '2022-03-11'

# Start date: to set start date of analysis
start_date <- '2020-11-01'

# Forecast start date: start of CDC forecast data (usually more recent than start_date)
forecast_start_date <- '2021-11-01'
```


## Download Datasets

## HHS Protect data downloaded weekly for report 'Region I COVID Hospital Utilization Analysis'
```{r}
df_raw <- read.csv('data/[Unified] Hospital Analytic.csv') %>%
  # Part of R1 is covered by the Albany, NY HRR - NY is included
  # Filtering by states can be removed/changed, but will take longer to run the larger the selection
    filter(state %in% c(target_states, 'NY')) %>%
		mutate(collection_date = as.Date(collection_date)) %>%
		filter(collection_date > start_date)
# Issues with file downloads - comment out below line as
# needed:
colnames(df_raw)[1] <- gsub('^...','',colnames(df_raw)[1])

summary(df_raw %>%
  select(hospital_pk, collection_date, total_beds, inpatient_beds, total_icu_beds)
  )
```

## CDC Ensemble Forecast
```{r}
inc_hosp_targets <- paste(0:130, "day ahead inc hosp")
forecasts_hosp <- load_forecasts(
  models = "COVIDhub-ensemble",
  dates = date_latest_forecast,
  date_window_size = 6,
  locations = target_statefips, #"US",
  types = c("point", "quantile"),
  targets = inc_hosp_targets,
  source = "zoltar",
  verbose = FALSE,
  as_of = NULL,
  hub = c("US")
)
```


## Population Breakdown
```{r}
df_population <- read_excel('data/NST-EST2021-POP.xlsx')

df_population$state <- state.abb[match(df_population$`State Name`, state.name)]
df_population <- df_population %>%
  mutate(state = ifelse(`State Name` == "District of Columbia", "DC", state))

df_population <- df_population %>%
  mutate(region = case_when(
    # state %in% R1states ~ "Region 1",
    state %in% target_states ~ "Selected States"
    ))

df_population_r <- df_population %>%
  group_by(region) %>%
  summarise(
    Population = sum(Population, na.rm = TRUE)
    , .groups = 'keep'
  )  
```


## Johns Hopkins (JHU) COVID Case Data
```{r}
# Download Case data for target FIPS
truth_incidence <- load_truth(
  truth_source = "JHU",
  target_variable = "inc case",
  temporal_resolution = "daily",
  locations = target_statefips
)

# Take 7-day moving average
daily_cases <- truth_incidence %>%
  rename(state = abbreviation) %>%
  rename(collection_date = target_end_date) %>%
  group_by(state) %>% 
  mutate(r = zoo::rollmean(value, k=7, fill=NA, align = 'right')/population * 1e5)

```

# Section 2: State-level Analysis

## Group and Summarize by State
```{r}
# Group and summarize HHS data by state
state_d <- df_raw %>%
  filter(state %in% target_states) %>%
  group_by(state, collection_date) %>%
  summarise(
            total_all_beds = sum(total_beds, na.rm = TRUE)
            , inpatient_all_beds = sum(inpatient_beds, na.rm = TRUE)
            , icu_all_beds = sum(total_icu_beds, na.rm = TRUE)
            , total_child_beds = total_all_beds - sum(all_adult_hospital_beds, na.rm = TRUE)
            , inpatient_child_beds = inpatient_all_beds - sum(all_adult_hospital_inpatient_beds, na.rm = TRUE)
            , icu_child_beds = icu_all_beds - sum(total_staffed_adult_icu_beds, na.rm = TRUE)
            , inpatient_all_beds_used = sum(inpatient_beds_used, na.rm = TRUE)
            , inpatient_child_beds_used = inpatient_all_beds_used - sum(all_adult_hospital_inpatient_bed_occupied, na.rm = TRUE)
            , icu_all_beds_used = sum(icu_beds_used, na.rm = TRUE)
            , icu_child_beds_used = icu_all_beds_used - sum(staffed_adult_icu_bed_occupancy, na.rm = TRUE)
            , total_child_beds_used_covid_confirmed = sum(total_pediatric_patients_hospitalized_confirmed_covid, na.rm = TRUE)
            , total_child_beds_used_covid = sum(total_pediatric_patients_hospitalized_confirmed_and_suspected_covid, na.rm = TRUE)
            , total_all_beds_used_covid = total_child_beds_used_covid + sum(total_adult_patients_hospitalized_confirmed_and_suspected_covid, na.rm = TRUE)
            , admission_child_covid_confirmed = sum(previous_day_admission_pediatric_covid_confirmed, na.rm = TRUE)
            , admission_child_covid = admission_child_covid_confirmed +
                                            sum(previous_day_admission_pediatric_covid_suspected, na.rm = TRUE)
            , admission_all_covid = admission_child_covid 
                                        + sum(previous_day_admission_adult_covid_suspected 
                                              + previous_day_admission_adult_covid_confirmed
                                              , na.rm = TRUE)
            , admission_confirmed_covid = admission_child_covid_confirmed 
                                        + sum(previous_day_admission_adult_covid_confirmed, na.rm = TRUE)
            , total_utilization = inpatient_all_beds_used/inpatient_all_beds
            , covid_deaths = sum(deaths_covid, na.rm = TRUE)
            , staffing_shortage_yes = sum(critical_staffing_shortage_today == 'true', na.rm = TRUE)
            , total_hosp_reporting = n()
            , .groups = 'keep')

# Moving average of the variables above
state_ma <- state_d[order(state_d$state, state_d$collection_date),] %>%
  group_by(state) %>%
  mutate(
            total_all_beds = rollmean(total_all_beds, k=7, fill=NA)
            , inpatient_all_beds = rollmean(inpatient_all_beds, k=7, fill=NA)
            , icu_all_beds = rollmean(icu_all_beds, k=7, fill=NA)
            , total_child_beds = rollmean(total_child_beds, k=7, fill=NA)
            , inpatient_child_beds = rollmean(inpatient_child_beds, k=7, fill=NA)
            , icu_child_beds = rollmean(icu_child_beds, k=7, fill=NA)
            , total_all_beds_used_covid = rollmean(total_all_beds_used_covid, k=7, fill=NA)
            , total_child_beds_used_covid_confirmed = rollmean(total_child_beds_used_covid_confirmed, k=7, fill=NA)
            , total_child_beds_used_covid = rollmean(total_child_beds_used_covid, k=7, fill=NA)
            , admission_all_covid = rollmean(admission_all_covid, k=7, fill=NA)
            , admission_child_covid_confirmed = rollmean(admission_child_covid_confirmed, k=7, fill=NA)
            , admission_child_covid = rollmean(admission_child_covid, k=7, fill=NA)
            , total_utilization = rollmean(total_utilization, k=7, fill=NA)
            , covid_deaths = rollmean(covid_deaths, k=7, fill=NA)
            ) 

state <- state_ma %>%
  pivot_longer(cols = -c(state, collection_date)
               , names_pattern = "(...*)_(...*)_beds", names_to = c("bedtype", "scope")) %>%
  mutate(bedtype=ifelse(bedtype=="", "value", bedtype)) 
# %>%  pivot_wider(names_from = 'scope', values_from = 'value')

```

## Join HHS data w/ other sources 
```{r}
# Census data
state_ma_census <- state_ma %>%
  inner_join(df_population, by = "state")

# JHU Case data
daily_cases_hosp <- state_ma_census %>%
  inner_join(daily_cases, by = c("state","collection_date"))

# JHU Truth + CDC Ensemble Forecast
truth_hosp <- load_truth(
  truth_source = "HealthData",
  target_variable = "inc hosp",
  locations = target_statefips # "US"
)

# 7-day Moving Average
truth_hosp_ma <- truth_hosp %>%
  filter(abbreviation %in% target_states) %>% # Filter for R1 states
  arrange(target_end_date) %>%
  ungroup() %>% group_by(abbreviation) %>% 
  mutate(admissions = zoo::rollmean(value, k = 7, align = "right", fill = NA))

# Data for CDC Ensemble Forecast plot
df_plot <- bind_rows(
            truth_hosp_ma 
            , forecasts_hosp %>%
                filter(type == 'quantile') %>%
                pivot_wider(names_from = quantile, names_prefix = 'quant', values_from = value)
      ) %>%
  filter(target_end_date > forecast_start_date #& !is.na(quant0.5)
         ) 


```

## Staffing Shortage Analysis ("Hospital Staffing Shortages" Slide)
```{r, fig.height=4, fig.width=6}
# Number of Hospitals Reporting lately
state_d %>%
  filter( state %in% target_states & collection_date > '2022-01-13') %>% 
  mutate(r = staffing_shortage_yes/total_hosp_reporting) %>%
  select(state, collection_date, r, total_hosp_reporting)

# Plot % of Hospitals per state reporting staffing shortages
state_d %>%
  filter( state %in% target_states & collection_date > start_date & collection_date <= date_most_hospitals_reported) %>% 
  mutate(r = staffing_shortage_yes/total_hosp_reporting) %>%
  ggplot(aes(x = collection_date, y = r)) + #, color = state
    facet_wrap(~ state, ncol = 2) + #scales = 'free_y' - For different axes
    geom_point(color = "grey55", size = 1) +
    geom_smooth(color = "blue", size = 1, span = 0.2) +
    labs(x = NULL, y= NULL, title = 'Percent of Hospitals Reporting Staffing Shortages') +
    scale_x_date(breaks = seq.Date(as.Date('2020-11-01'), as.Date('2022-03-01'), "2 month"), date_labels =  "%b %d %Y") +
    scale_y_continuous(labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 60, hjust=1))
```

## COVID Case Incidence per state ("COVID Incidence" Slide)
```{r, fig.height=4, fig.width=6}
# Plot COVID Incidence per 100k people
daily_cases_hosp %>%
  filter(location %in% target_statefips & collection_date > start_date) %>% 
  ggplot(aes(x = collection_date, y = r)) + 
    facet_wrap(~ state, ncol = 2) + 
    # geom_line(color = "blue", size = 1) +
    geom_point(color = "gray45", size = 1) +
    geom_smooth(color = "blue", size = 1, span = 0.02, se = FALSE) +
    labs(x = NULL, y = NULL, title = 'COVID-19 Daily Cases per 100K People, 7-day Moving Average') +
    scale_x_date(breaks = seq.Date(as.Date('2020-11-01'), as.Date('2022-03-01'), "2 month"), date_labels =  "%b %d %Y") +
    scale_y_continuous(limits = c(0, 400))

# Get most recent values for COVID cases - for "COVID Incidence" slide
# Pull out most recent case values
current_state_cases <- daily_cases_hosp %>%
  filter(state %in% target_states & collection_date == date_case_count) %>% 
  select(r)

# National Incidence Data
truth_incidence_US <- load_truth(
  truth_source = "JHU",
  target_variable = "inc case",
  locations = "US"
)

# National Cases Per 100k people
current_US_cases <- truth_incidence_US %>%
  mutate(incday100K = value / population * 1e5 / 7) %>%
  filter(target_end_date == max(target_end_date)) %>%
  select(location, target_end_date, value, incday100K)
```

## State-level Summary/Resource Prioritization ("State Summary" Slide) (RETIRED - NOT USED)
```{r}
# Create State Summary Table
state_summary <- daily_cases_hosp %>%
  filter(state %in% target_states) %>%
  filter(!is.na(total_utilization)) %>%   
  group_by(state) #%>%

# Add Hospital utilization Column
cols <- c('state', paste('Hospital Utilization as of', date_most_hospitals_reported))
state_summary <- state_summary %>%
  filter(collection_date == date_most_hospitals_reported) %>%
  select(state, total_utilization)
colnames(state_summary) <- cols
  
# Add Daily New Cases (per 100k) Column
tmp <- daily_cases_hosp %>%
  filter(state %in% target_states) %>%
  #mutate(inc100k = (daily_cases/Population)*100000) %>%
  filter(!is.na(r)) %>%
  group_by(state) #%>%

cols <- c('state', paste('New Cases per 100K as of', date_case_count))
tmp <- tmp %>%
  filter(collection_date == date_case_count) %>%
  select(state, r)
colnames(tmp) <- cols

state_summary <- state_summary %>%
  inner_join(tmp, by = c('state'))

# Add Hospital Admissions (per 100k) Column
tmp <- state_ma_census %>%
  filter(state %in% target_states) %>%
  mutate(r = (admission_all_covid/Population)*100000) %>%
  filter(!is.na(r)) %>%
  group_by(state) #%>%

cols <- c('state', paste('Hosp. Admissions per 100K as of', date_most_hospitals_reported))
tmp <- tmp %>%
  filter(collection_date == date_most_hospitals_reported) %>%
  select(state, r)
colnames(tmp) <- cols

state_summary <- state_summary %>%
  inner_join(tmp, by = c('state'))

# Add Critical Staffing Shortage Reported Column
tmp <- state_d %>%
  filter( state %in% target_states) %>%
  mutate(r = staffing_shortage_yes/total_hosp_reporting) %>%
  filter(total_hosp_reporting > 5 & !is.na(r)) %>%
  group_by(state) %>%
  filter(collection_date == date_most_hospitals_reported) %>%
  select(state, r)
colnames(tmp) <- c('state', paste('Staffing Shortage as of', date_most_hospitals_reported))

state_summary <- state_summary %>%
  inner_join(tmp, by = c('state')) #%>%

state_summary %>%
  kableExtra::kbl() %>% kableExtra::kable_styling()
```

## CDC Ensemble Forecasts per State ("CDC Ensemble Forecast" Slide)
```{r, fig.height=4,fig.width=6}
plotFcst <- function(tit, df_plot, ylims){
  brks <- sort(c(seq.Date(as.Date('2021-11-01'), as.Date('2022-04-01'), "1 month"),
                seq.Date(as.Date('2021-11-15'), as.Date('2022-04-01'), "1 month")))
ggplot(df_plot, aes(x = target_end_date)) +
    facet_wrap(~ abbreviation, ncol = 2, scales = 'free_y') + # - For different axes
    geom_line(aes(y = admissions, color = "Reported (with 7-d mov. average)"), size = 1) +
    geom_point(aes(y = value, color = "Reported (with 7-d mov. average)"), size = 1.5) +
    scale_color_manual(name = NULL, values = c("blue")) +
    geom_ribbon(aes(ymin = quant0.025, ymax = quant0.975, fill = "95% Prediction Interval"), size = 1) +
    geom_ribbon(aes(ymin = quant0.25, ymax = quant0.75, fill = "50% Prediction Interval"), size = 1) +
    scale_fill_manual(name = NULL, values = c("salmon3", "salmon1", "orangered4")) +
    geom_point(aes(y = quant0.5), color = "orangered4", size = 1) +
    geom_line(aes(y = quant0.5, fill = "Ensemble"), size = 1) +
    labs(x = NULL, y = NULL, title = tit) +
    expand_limits(y = ylims) +
    scale_x_date(breaks = brks, date_labels =  "%b %d %Y") +
    guides(color = guide_legend(order=1),
         fill = guide_legend(order=2)) +
    theme(axis.text.x = element_text(angle = 60, hjust=1))
}

plotFcst('New Hospital Admissions per day', df_plot, c(0, 100))
```

## COVID Deaths per State ("COVID Deaths" Slide)
```{r, fig.height=4,fig.width=6}
# Load JHU Truth for deaths
truth_death <- load_truth(
  truth_source = "JHU",
  target_variable = "inc death",
  locations = target_statefips
)

# Plot COVID weekly deaths per 100k people
truth_death %>%
  filter(target_end_date > start_date) %>%
  mutate(r = value/population * 1e5) %>%
ggplot(aes(x = target_end_date, y = r)) +
    facet_wrap(~ abbreviation, ncol = 2) + # , scales = 'free_y' - For different axes
    geom_point(color = "grey45", size = 1) +
    geom_smooth(color = "blue", size = 1, span = 0.1, se = FALSE) +
    labs(x = NULL, y = NULL, title = 'COVID-19 Weekly Deaths per 100K people') +
    scale_x_date(breaks = seq.Date(as.Date('2020-11-01'), as.Date('2022-03-01'), "2 month"), date_labels =  "%b %d %Y") +
    theme(axis.text.x = element_text(angle = 60, hjust=1))

# Get current values for COVID deaths - for "COVID Deaths" slide output
# Get most recent values for weekly deaths by state (raw and per 100k)
current_state_deaths <- truth_death %>%
  filter(target_end_date > '2022-01-10') %>%
  mutate(r = value/population * 1e5) %>%
  select(target_end_date, location_name, r, value)

# National COVID Deaths
truth_death_US <- load_truth(
  truth_source = "JHU",
  target_variable = "inc death",
  locations = "US"
)
  
# Deaths Per 100k people
Current_US_deaths <- truth_death_US  %>%
  tail(n = 1) %>%
  mutate(per100K = value / population * 1e5) %>%
  select(model, location, target_end_date, value, population, per100K)
```



# Section 3: HRR-level Analysis

## Aggregate by HRR
```{r}
hrr_d <- df_raw %>%
  group_by(hrr, collection_date) %>%
  summarise(
            total_all_beds = sum(total_beds, na.rm = TRUE)
            , inpatient_all_beds = sum(inpatient_beds, na.rm = TRUE)
            , icu_all_beds = sum(total_icu_beds, na.rm = TRUE)
            , total_child_beds = total_all_beds - sum(all_adult_hospital_beds, na.rm = TRUE)
            , inpatient_child_beds = inpatient_all_beds - sum(all_adult_hospital_inpatient_beds, na.rm = TRUE)
            , icu_child_beds = icu_all_beds - sum(total_staffed_adult_icu_beds, na.rm = TRUE)
            , inpatient_all_beds_used = sum(inpatient_beds_used, na.rm = TRUE)
            , inpatient_child_beds_used = inpatient_all_beds_used - sum(all_adult_hospital_inpatient_bed_occupied, na.rm = TRUE)
            , icu_all_beds_used = sum(icu_beds_used, na.rm = TRUE)
            , icu_child_beds_used = icu_all_beds_used - sum(staffed_adult_icu_bed_occupancy, na.rm = TRUE)
            , total_child_beds_used_covid_confirmed = sum(total_pediatric_patients_hospitalized_confirmed_covid, na.rm = TRUE)
            , total_child_beds_used_covid = sum(total_pediatric_patients_hospitalized_confirmed_and_suspected_covid, na.rm = TRUE)
            , total_all_beds_used_covid = total_child_beds_used_covid + sum(total_adult_patients_hospitalized_confirmed_and_suspected_covid, na.rm = TRUE)
            , admission_child_covid_confirmed = sum(previous_day_admission_pediatric_covid_confirmed, na.rm = TRUE)
            , admission_child_covid = admission_child_covid_confirmed +
                                            sum(previous_day_admission_pediatric_covid_suspected, na.rm = TRUE)
            , admission_all_covid = admission_child_covid 
                                        + sum(previous_day_admission_adult_covid_suspected 
                                              + previous_day_admission_adult_covid_confirmed
                                              , na.rm = TRUE)
            , admission_confirmed_covid = admission_child_covid_confirmed 
                                        + sum(previous_day_admission_adult_covid_confirmed, na.rm = TRUE)
            , non_child_covid_utilization = ((icu_all_beds_used + inpatient_all_beds_used) - total_child_beds_used_covid)/total_all_beds
            , non_covid_utilization = (inpatient_all_beds_used - total_all_beds_used_covid)/inpatient_all_beds
            , covid_utilization = total_all_beds_used_covid/inpatient_all_beds
            , util_ratio = covid_utilization/non_covid_utilization
            # , total_utilization = (inpatient_all_beds_used)/total_all_beds
            , total_utilization = inpatient_all_beds_used/inpatient_all_beds
            , covid_ratio = covid_utilization/total_utilization
            , icu_utilization = icu_all_beds_used/icu_all_beds
            , general_utilization = (inpatient_all_beds_used-icu_all_beds_used)/(inpatient_all_beds-icu_all_beds)
            , covid_deaths = sum(deaths_covid, na.rm = TRUE)
            , .groups = 'keep')

# moving average of the variables above
hrr_ma <- hrr_d[order(hrr_d$hrr, hrr_d$collection_date),] %>%
  group_by(hrr) %>%
  mutate(
            total_all_beds = rollmean(total_all_beds, k=7, fill=NA)
            , inpatient_all_beds = rollmean(inpatient_all_beds, k=7, fill=NA)
            , icu_all_beds = rollmean(icu_all_beds, k=7, fill=NA)
            , total_child_beds = rollmean(total_child_beds, k=7, fill=NA)
            , inpatient_child_beds = rollmean(inpatient_child_beds, k=7, fill=NA)
            , icu_child_beds = rollmean(icu_child_beds, k=7, fill=NA)
            , total_all_beds_used_covid = rollmean(total_all_beds_used_covid, k=7, fill=NA)
            , total_child_beds_used_covid_confirmed = rollmean(total_child_beds_used_covid_confirmed, k=7, fill=NA)
            , total_child_beds_used_covid = rollmean(total_child_beds_used_covid, k=7, fill=NA)
            , admission_all_covid = rollmean(admission_all_covid, k=7, fill=NA)
            , admission_child_covid_confirmed = rollmean(admission_child_covid_confirmed, k=7, fill=NA)
            , admission_child_covid = rollmean(admission_child_covid, k=7, fill=NA)
            , non_child_covid_utilization = rollmean(non_child_covid_utilization, k=7, fill=NA)
            , total_utilization = rollmean(total_utilization, k=7, fill=NA)
            , icu_utilization = rollmean(icu_utilization, k=7, fill=NA)
            , general_utilization = rollmean(general_utilization, k=7, fill=NA)
            , covid_deaths = rollmean(covid_deaths, k=7, fill=NA)
            ) 
```

## Divide into Target HRRs
```{r}
# NOTE: The encoding below is specific to R1 and can be changed as needed
hrr_d_tar <- hrr_d %>%
  filter( hrr %in% target_hrrs & collection_date > start_date) 
hrr_d_tar$hrr <- factor(hrr_d_tar$hrr, levels = target_hrrs)
hrr_d_tar <- hrr_d_tar%>%
  mutate(hrr=recode(hrr,'109' = 'CT - Bridgeport',
                        '110'	= 'CT - Hartford',
                        '111'	= 'CT - New Haven',
                        '221'	= 'ME - Bangor',
                        '222'	= 'ME - Portland',
                        '227'	= 'MA - Boston',
                        '230'	= 'MA - Springfield',
                        '231'	= 'MA - Worcester',
                        '281'	= 'NH - Lebanon',
                        '282'	= 'NH - Manchester',
                        '295'	= 'NY - Albany',
                        '364'	= 'RI - Providence',
                        '424'	= 'VT - Burlington'))
```

## Hospital Utilization Rates by HRR ("Hospital Utilization" Slide)
```{r, fig.height=4,fig.width=6}
# Plot total utilization by HRR
hrr_d_tar %>%
  filter(collection_date <= date_most_hospitals_reported) %>%
  ggplot(aes(x = collection_date, y = total_utilization)) + #, color = state
    facet_wrap(~ hrr, ncol = 3) + #scales = 'free_y' - For different axes
    geom_hline(yintercept = 0.8, color = 'orange', linetype='dashed') +
    geom_line(color = "blue", size = 1) +
    labs(x = NULL, y = NULL, title = 'COVID-19 Total Hospital Utilization') +
    scale_x_date(breaks = seq.Date(as.Date('2020-11-01'), as.Date('2022-03-01'), "2 month"), date_labels =  "%b %d %Y") +
    scale_y_continuous(labels=scales::percent, limits = c(0, 1)) +
    theme( text = element_text(size=12)) +
    theme(axis.text.x = element_text(angle = 60, hjust=1))

# Pull current utilization values
current_hrr_util <- hrr_d_tar %>%
  filter(collection_date == date_most_hospitals_reported) %>%
  select(hrr,collection_date,total_utilization)
```


## COVID vs. Non-COVID utilization (RETIRED - NOT USED)
```{r}
hrr_d_tar %>%
  ggplot() + # color = state
    facet_wrap(~ hrr, ncol = 3) + #scales = 'free_y' - For different axes
    geom_line(aes(x = collection_date, y = total_utilization, color="Total Utilization")) + 
    geom_line(aes(x = collection_date, y = non_covid_utilization, color = "Non-COVID-19 Utilization")) +
    geom_ribbon(aes(ymin = non_covid_utilization, ymax = total_utilization, x=collection_date), fill="blue") + 
    labs(x = NULL, y = NULL, title = 'COVID-19 Hospital Utilization') +
    scale_x_date(breaks = seq.Date(as.Date('2020-11-01'), as.Date('2022-03-01'), "2 month"), date_labels =  "%b %d %Y") +
    scale_y_continuous(labels=scales::percent) +
    theme( text = element_text(size=12)) +
    theme(axis.text.x = element_text(angle = 60, hjust=1))
```

## COVID Utilization by HRR ("COVID Hospital Utilization" Slide)
```{r, fig.height=4,fig.width=6}
# Plot percent of beds being used by COVID patients
hrr_d_tar %>%
  filter(collection_date <= date_most_hospitals_reported) %>%
  ggplot(aes(x = collection_date, y = covid_utilization)) + #, color = state
    facet_wrap(~ hrr, ncol = 3) + #scales = 'free_y' - For different axes
    geom_line(color = "blue", size = 1) +
    labs(x = NULL, y = NULL, title = 'COVID Utilization per HRR') +
    scale_x_date(breaks = seq.Date(as.Date('2020-11-01'), as.Date('2022-03-01'), "2 month"), date_labels =  "%b %d %Y") +
    scale_y_continuous(labels=scales::percent) +
    theme( text = element_text(size=12)) +
    theme(axis.text.x = element_text(angle = 60, hjust=1))

# Pull most recent COVID utilization values
current_covid_util <- hrr_d_tar %>%
  filter(collection_date == date_most_hospitals_reported) %>%
  select(hrr,collection_date,covid_utilization)
```



